My title

### 2024-11-28 paper/paper.qmd
finished discussion

library(tidyverse)
library(palmerpenguins)
library(kableExtra)
library(arrow)
library(readr)
library(rstanarm)
library(modelsummary)

@@

Table 2 (CITATION) shows a summary of detailed statistics about the cleaned dataset. It showed that books that were considered "high rated" had more pages on average than low rated books. Furthermore, high rated books were on average published 2 years before low rated books, around the year 2003. In addition to this, the amount of ratings high-rated books received far exceed low rated books, at about 4x. The most common type of book cover also turned out to be hard covers. These variables are key in the analysis, and are further shown in (CITE HERE)

@@

summary_table <- data %>%
  filter(!is.na(rated_high)) %>%  
  group_by(rated_high) %>%       
  summarise(
    avg_pages = mean(pages, na.rm = TRUE),          
    avg_publish_year = mean(publish_year, na.rm = TRUE),
    avg_rating_count = mean(rating_count, na.rm = TRUE),
    avg_cover = names(sort(table(cover), decreasing = TRUE)[1])
  )

@@

data2 <- data %>% filter(rating >= 4)

ggplot(data2, aes(y = cover)) + 
  geom_bar() +
  theme_minimal()

@@

After running the regression model above, we receive the coefficient values showcased in Table X.

@@

@@

```{r}
#| label: summary_statistic_cleaned_dataset2
#| fig-cap: "Summary Statistic of the Cleaned Dataset"
#| echo: false

data2 <- data %>% filter(rating >= 4)

ggplot(data2, aes(x = rating, y = rating_count)) +
  geom_point()

ggplot(data2, aes(x = rating, y = pages)) +
  geom_point()

@@

@@

-->
# References

>>>>

library(tidyverse)
library(palmerpenguins)
library(kableExtra)
library(arrow)
library(readr)
library(rstanarm)
library(modelsummary)
library(dplyr)

@@

Table 2 (CITATION) shows a summary of detailed statistics about the cleaned dataset. It showed that books that were considered "high rated" had more pages on average than low rated books. Furthermore, high rated books were on average published 2 years before low rated books, around the year 2003. In addition to this, the amount of ratings high-rated books received far exceed low rated books, at about 4x. Kindle covers had the highest proportion of "high-rated" books out of any other cover types. These variables are key in the analysis, and are further shown in (CITE HERE)

@@

summary_table <- data %>%
  filter(!is.na(rated_high)) %>%  
  group_by(rated_high) %>%       
  summarise(
    avg_pages = mean(pages, na.rm = TRUE),          
    avg_publish_year = mean(publish_year, na.rm = TRUE),
    avg_rating_count = mean(rating_count, na.rm = TRUE),
    highest_proportion_cover = data %>%
      group_by(cover) %>%
      summarise(high_rated_pct = mean(rated_high, na.rm = TRUE)) %>%
      slice_max(high_rated_pct, n = 1) %>%
      pull(cover)
  )

@@

data2 <- data %>%filter(rating >= 4)

cover_proportions <- data %>%
  group_by(cover) %>%
  summarise(high_rated_pct = mean(rated_high, na.rm = TRUE)) %>%
  arrange(desc(high_rated_pct))  # Sort by highest proportion

# Create the horizontal bar plot
ggplot(cover_proportions, aes(x = high_rated_pct, y = reorder(cover, high_rated_pct), fill = high_rated_pct)) +
  geom_bar(stat = "identity", show.legend = FALSE) +
  labs(
    title = "Proportion of High-Rated Books by Cover Type",
    x = "Proportion of High-Rated Books",
    y = "Cover Type"
  ) +
  scale_x_continuous(labels = scales::percent_format()) +  # Format x-axis as percentages
  theme_minimal() +
  theme(
    axis.text = element_text(size = 10),
    plot.title = element_text(hjust = 0.5, size = 14)
  )

@@

After running the regression based on the model shown above, we get the coefficient values showcased in Table X (CITE HERE).

COEFFICIENT RANGE (CITE) represent the 90% probability intervals of the estimates, where a coefficient is considered statistically significant if the range excludes 0. In addition to this, these coefficients are expressed in log-odds, meaning it suggests a positive association with a book being "highly-rated" when positive and "low-rated" when negative.

With this in mind, we can see that, the Kindle Edition cover type had the highest correlation with a book being "highly-rated", assuming all else held constant, reflecting the analysis that was seen in DATA (CITE HERE). In contrast, the number of pages of a book, and the number of ratings no statistically significant influence on a book being "highly-rated".

Although the publish year was not statistically significant according to the GRAPH (CITE), it exhibited a slight negative relationship (coefficient: -0.01), consistent with previous findings (CITE) that "high-rated" books tend to have earlier publication years compared to "low-rated" ones.

```{r}
#| label: summary_statistic_cleaned_dataset3
#| fig-cap: "Summary Statistic of the Cleaned Dataset"
#| echo: false

modelsummary(
  list (
    "Book is High-Rated" = model_file
  ),
  statistic = "mad"
)
```

@@

## Rating Count and Page Count

As shown by SECTIOM  (RESULTS), the number of ratings a book receives and its page length had no statistical significance on a book being highly-rated. In particular, these factors are likely independent of how readers perceive its quality or enjoyment. Short books can be impactful and concise, whereas longer books can offer richer detail.

Furthermore, the irrelevance of the number of ratings a book receives could be explained by herd effect; where readers rely on the ratings and reviews of others to make their own rating decisions. Therefore, once a book has many reviews, its average rating stabilizes, making the number of ratings irrelevant to the overall evaluation.

## Type of Cover

The results in SECTION (RESULTS), indicated a big positive relationship between book cover types and its "highly-rated" status. In particular, the "Kindle Edition" book cover had the highest coefficient (NUMBER HERE). A potential explanation could be that ebooks (such as Kindle Edition) are often preferred over physical books for their convenience, affordability and accessibility. Additionally ebooks are often cheaper due to saving material costs and saving physical space. In Middle-Eastern countries, 74.6% students preferred e-books in terms of easy to carry and 80.6% of them spent more time reading from e-books than printed books (CITATION HERE). Thus, it could appear that e-books have an advantage in attracting those seeking convenience and personalization in their reading, potentially explaining its high-rating over any other book cover types.

## Publish Year

While the result in SECTION (RESULT) showed that the publish year was statistically insignificant, (GRAPH) a small negative correlation which was expected. In particular, high-rated books had an older publish year than lowly-rated books.

The first explanation could be that older books have had more time to be appreciated, analyzed and critiqued, which could allow their work to be better established than current generation books. Many older books that receive high ratings have stood the test of time, becoming classics that made its name for generations.

The second explanation could be that older books may benefit from nostalgia, where readers could assign higher ratings due to a stronger emotional connection and cultural significance they hold. While this

@@

@@

## Posterior Predictive Check

We used a posterior predictive check in FIGURE (CITE) to evaluate how well the model fits the data. This compares the observed data Y (CHANGE) against the replicated data y-REP (CHANGE) which was generated by our model in SECTION 3 (CITE). The poterior distribution fitting perfectly suggests that the Bayesian logistic regression model is a good model fit.

@@

modelplot(model_file, conf_level = 0.9, coef_omit = c(5,8)) +
  labs(x= "90% percent credibility interval")
```

# References
